Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-26 paper/paper.tex
checkpointing
Bibliography fixes
Add minor revisions mostly to section 5

% TODO: add in the referee tag for the submission
%\documentclass[global,twocolumn,referee]{svjour}
\documentclass[global,twocolumn]{svjour}
\usepackage{cite}
\usepackage{amsmath}
% \usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{url}
\usepackage{comment}
\usepackage{paralist}
\usepackage{graphicx}
\graphicspath{{./figs/}}
\usepackage{listings}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{flushend}
\usepackage{hyperref}
\usepackage[firstpage]{draftwatermark}
\usepackage[lighttt]{lmodern}
\usepackage[normalem]{ulem}

@@

\ifREVISIONS
\subsection{Revisions}
\begin{compactitem}
  \item \sout{Add in the AGREE specification for the system}
  \item \sout{Add in the AGREE verification conditions (e.g., similar to those in the Scheduled Components NFM submission)}
  \item \sotu{Add reference to the Liskov principle of safe-substitution when stating that the system contract is a sound abstraction of the implementation.}
  \item Add back in a few sentences on the contract for the filter since those have been removed with the addition of the formal definitions.
\end{compactitem}
\fi

\section{Code contracts for cyber components}
\label{code-contracts}
\input{high-assurance-contracts}

@@

%% \section{Synthesis from code contracts}
%% \label{sec:semantics}
%% \input{semantics}

\ifREVISIONS
\subsection{Revisions}
\begin{compactitem}
  \item Add in intuitive definition or AGREE leaf-component semantics
  \item State well-formed theorem
  \item State correctness theorem or any key theorems to the synthesis proof
\end{compactitem}
\fi

>>>>

% TODO: add in the referee tag for the submission
%\documentclass[global,twocolumn,referee]{svjour}
\documentclass[global,twocolumn,keeplastbox]{svjour}
\usepackage{cite}
\usepackage{amsmath}
% \usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{url}
\usepackage{comment}
\usepackage{paralist}
\usepackage{graphicx}
\graphicspath{{./figs/}}
\usepackage{listings}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{flushend}
\usepackage{hyperref}
\usepackage[firstpage]{draftwatermark}
\usepackage[lighttt]{lmodern}
\usepackage[normalem]{ulem}

@@

\section{Code contracts for cyber components}
\label{sec:code-contracts}
\input{high-assurance-contracts}

@@
